Predicting detection probabilities for rare and undersampled North American landbirds

### 2023-10-24 article/article.tex
writing some of distance discussion

\subsection{Distance Modelling}
\par Estimates of EDR also changed very little from species that were originally modelled by the single-species models in \citet{edwards_point_2023}, to the same ones modelled in the multi-species model here.
However, there was evidence for an average small downward shift in EDRs when modelled under a multi-species context.
Still, the 5-fold cross validation tended to show little to no preference for one more or another when the sample size was large, and a slight (but still very small) preference for the multi-species model when the sample size was smaller.
There was less evidence for the multi-species model being able to improve the precision of EDR estimates across sample sizes, indicating that a single-species model may mostly be sufficient for precise estimates.
Under this context, it would appear that a multi-species model may slightly bring down estimates of EDR for species with a smaller sample size.

\par Talk about species with a large relative difference

\par Talk about parameters

@@

* talk about Bicknell's Thrush removal and distance modelling

>>>>

\subsection{Distance Modelling}
\par Estimates of EDR also changed very little from species that were originally modelled by the single-species models in \citet{edwards_point_2023}, to the same ones modelled in the multi-species model here.
However, there was evidence for an average small downward shift in EDRs when modelled under a multi-species context.
Still, the 5-fold cross validation tended to show almost no preference for one model or another when the sample size was large, and a slight (but still very small) preference for the multi-species model when the sample size was small.
There was less evidence for the multi-species model being able to improve the precision of EDR estimates across sample sizes, indicating that a single-species model may mostly be sufficient for precise estimates.
Under this context, it would appear that a multi-species model may slightly bring down estimates of EDR for species with a smaller sample size.

\par There were six species where the relative difference in EDR between the single-species model and multi-species model was over 20\%. Unlike removal modelling, these species (Sharp-tailed Grouse, Sedge Wren, Ring-necked Pheasant, Chimney Swift, Boat-tailed Grackle, and Baird's Sparrow) had little in common with each other in terms of sample size (range of 227 for Boat-tailed Grackle through 4466 for Baird's Sparrow) and EDR (ranging from 50.8 m to 226 m in single-species, and from 73.2 m to 159.1 m in the multi-species model). 
Additionally, there was mixed support among these species for single-species vs. multi-species: Chimney Swift and Boat-tailed Grackle had the multi-species model preferred, whereas the others had the single-species model preferred.
It could be noted that both Chimney Swift and Boat-tailed Grackle showed an increase in estimated EDR from single-species to multi-species modelling and preferred the multi-species model, but Baird's Sparrow also showed an increase and preferred the single-species model.

\par Similar to removal modelling, we found less support than \citet{solymos_phylogeny_2018} for migration strategy having an effect on EDR, although the posterior distribution for both the resident and migrant species were much further away from zero, indicating at least some support.
Habitat type, body mass, and song pitch, as expected, all had an overall effect on EDR, as was found in \citet{solymos_phylogeny_2018} and \cite{johnston_species_2014}.

@@

\par We generated predictions of cue rate for seven species of landbirds that are listed on Partners in Flight's watchlist: Spotted Owl, Bicknell's Thrush, LeConte's Thrasher, Tricoloured Blackbird, Harris's Sparrow, Kirtland's Warbler, and Lesser Prairie-chicken. 
For all species except Bicknell's Thrush and Kirtland's Warbler, we had at least some samples, but fewer than the minimum threshold of 75 for NA-POPS.
For these five species, we used the multi-species model as a way to relax the sample size requirements by allowing for the sharing of information among related species via phylogeny.
For Bicknell's Thrush and Kirtland's Warbler, we had zero samples, and so we used the multi-species model purely to predict estimates of cue rate, again based off of information sharing from similar species.

Overall, the estimates of cue rate fell roughly where we would expect based on related species.
For example, Harris's Sparrow (n = 65) had an estimated cue rate of 0.30 cues per minute, with a 95\% credible interval of [0.21, 0.42].
